INSTRUCTION SETS FOR STRANGERS

### 2021-09-30 instructionsetsforstrangers/instructionsetsforstrangers.tex
link to wavemachine video

Next we found some $1/8$ inch and $3/4$ inch plywood and created the base of the new mechanishm. At this point we also determined the best way to make the handle to activate the hand waving easier to use. A handle that needs to be pulled is ambiguous and not very visual, so we decided to make the handle another lever in the shape of a hand that would encourage users to use their hands to activate it. This was a simple lever that sticks out of one side of the mechanism pulled one side of the hand waving lever down when activated. \href{https://drive.google.com/file/d/1A4jMRefTUcI-PZPhbS6XSqFU6V4kzS8j/view?usp=sharing}{Link to video of lever action.}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth, angle=270]{"images/III/leverwithbase.jpg"}
\caption{Big hands!}
\end{figure}

@@

>>>>

Next we found some $1/8$ inch and $3/4$ inch plywood and created the base of the new mechanishm. At this point we also determined the best way to make the handle to activate the hand waving easier to use. A handle that needs to be pulled is a bit ambiguous and not very visual, so we decided to make the handle another lever in the shape of a hand that would encourage users to use their hands to activate it. This was a simple lever that sticks out of one side of the mechanism pulled one side of the hand waving lever down when activated. \href{https://drive.google.com/file/d/1A4jMRefTUcI-PZPhbS6XSqFU6V4kzS8j/view?usp=sharing}{Link to video of lever action.}

\begin{figure}[ht!]
\centering
\includegraphics[width=0.5\textwidth, angle=270]{"images/III/leverwithbase.jpg"}
\caption{Lever action.}
\end{figure}

@@

takeaways

no one wants to push hard on the hands

people who were more intoxicaed we re less gentle
